\documentclass[landscape,twocolumn,12pt]{article}

\usepackage[margin=0.1in]{geometry}
\usepackage{xifthen}

\usepackage{xparse}

\newcounter{qs}

\DeclareExpandableDocumentCommand{\q}{m}{\vspace*{\fill}\parbox[c][][c]{0.4\textwidth}{\Huge #1}\vspace*{\fill} \addtocounter{qs}{1} \ifthenelse{\value{qs} = 3}{\newpage \setcounter{qs}{0}}{}}

\DeclareExpandableDocumentCommand{\ba}{m}{{\em #1}}

\begin{document}
\begin{center}

\q{What year did ARPANET migrate to TCP/IP, creating what would be the Internet?}
\q{In 2013 lava is flowing from the Kilauea volcano on Hawaii's Big Island. What year did this eruption start?}
\q{In what year was the final episode of M*A*S*H aired?}
\q{In what year did Michael Jackson first perform the ``moonwalk''?}
\q{In what year did Tokyo Disneyland open?}
\q{In what year did the first man-made object leave the vicinity of the planets of the Solar System? (Bonus: What was the object? \ba{Pioneer 10})}
\q{In what year did the product that became the Nintendo Entertainment System launch? (Bonus: What was its original name? \ba{The Nintendo Family Computer, or Famicom})}
\q{In what year was GPS declassified for civilian use? (Bonus: Who made this announcement? \ba{President Ronald Reagan})}
\q{In what year was the first African-American crowned Miss America? (Bonus: Who was it? \ba{Vanessa Williams})}
\q{In what year was the GNU Project announced? (Bonus: What does GNU stand for? \ba{GNU's Not Unix})}
\q{In what year was Martin Luther King, Jr. Day created?}
\q{In what year was DARE launched? (Bonus: What does DARE stand for? \ba{Drug Abuse Resistance Education})}
\q{In what year was the McNugget invented?}
\q{In what year was the first minivan produced? (Bonus: What was it? \ba{The Dodge Caravan and Plymouth Voyager})}
\q{In what year was the last DeLorean produced?}
\q{In what year did the last King of Italy die? (Bonus: What was his name? \ba{Umberto II})}
\q{In what year did the last survivor of the Titanic die? (Bonus: Who were they? \ba{Sid Daniels})}
\q{In what year was Aesop's Fables translated into Latin?}
\q{What is the largest number such that all coprimes smaller than itself are prime?}
\q{How many sides does a tricontagon have?}
\q{What is the atomic number of zinc?}
\q{How many major and minor keys are there in Western tonal music?}
\q{What is the minimum age of United States senators?}
\q{What wedding anniversary is the ``pearl'' anniversary?}
\q{What is in the international calling code for Greece?}
\q{How many tracks are on ``The White Album''? (Bonus: What is the 30th track? \ba{Good Night}) (Bonus Bonus: Who sings it? \ba{Starr})}
\q{How many pieces of silver was Judas Iscariot paid?}
\q{If you have scored twice on your opponent in tennis, how many points do you have?}
\q{How many teams are in the MLB, NBA, and NHL?}
\q{How many states were there in the United States in 1848? (Bonus: What was the 30th state? \ba{Wisconsin})}
\q{In what year was  Kate Bosworth born? (Bonus: Who is she? \ba{She plays Lois Lane.})}
\q{In what year was Michelle Branch born?}
\q{In what year was Chris Hemsworth born? (Bonus: Who is he? \ba{He plays Thor.})}
\q{In what year was Jon Lech Johnson born? (Bonus: Who is he? \ba{He cracked the DVD encryption system, as well as FairPlay, Apple Lossless. WMV9, among other DRM formats.})}
\q{In what year did the creator of Tintin die? (Bonus: Who is it? \ba{George Prosper Remi})}
\q{In what year did the heaviest human being ever recorded die? (Bonus: How heavy was he? \ba{1400 lbs}) (Bonus Bonus: How old was he? \ba{41})}

\end{center}
\end{document}
